KidsAIR initial SUMs data work

### 2020-01-14 home_char_act_cleaning.Rmd
cleaning joining datasets begin summarizing data

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Clean up all home characteristics data
```{r}
kids_home_char <- read_rds("Output/kids_home_char.rds")

kids_home_char_clean <- kids_home_char

# write_rds(kids_home_char_clean, "Output/kids_home_char_clean.rds")
```

@@

# Clean up all home activity data
```{r}
kids_home_act <- read_rds("Output/kids_home_act.rds")

kids_home_act_clean <- kids_home_act

# write_rds(kids_home_act_clean, "Output/kids_home_act_clean.rds")
```

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Clean up all home characteristics data
```{r}
kids_home_char <- read_rds("Output/kids_home_char.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(home_char_clean, "Output/home_char_clean.rds")
```

# Summary data for home characteristics
```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds")

# Summarize numeric vars
home_char_summary <- home_char_clean %>% 
  group_by(area) %>% 
  summarize(mean(home_sqft, na.rm = TRUE), 
            min(home_sqft, na.rm = TRUE), 
            median(home_sqft, na.rm = TRUE), 
            max(home_sqft, na.rm = TRUE))
home_char_summary

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_char_clean %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -home_sqft, -stove_model) 
lapply(table_list, table)

## Select specific var to assess individually/group by area
table(table_list$residents_total, table_list$area, useNA = "ifany")
```

@@

# Clean up all home activity data
```{r}
kids_home_act <- read_rds("Output/kids_home_act.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

home_act_clean <- kids_home_act %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(home_act_clean, "Output/home_act_clean.rds")
```

# Summary data for home characteristics
```{r}
# Load dataset
home_act_clean <- read_rds("Output/home_act_clean.rds")

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -home_act_comments) 
lapply(table_list, table)

## Select specific var to assess individually/group by area
table(table_list$home_act_sweep, table_list$area, useNA = "ifany")
```

### 2020-01-14 indoor_temp_rh_cleaning.Rmd
cleaning joining datasets begin summarizing data

---
title: "KidsAIR indoor temp and humidity cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Clean up all temp/rh data
```{r}
kids_indoor_temp_rh <- read_rds("Output/kids_indoor_temp_rh.rds")

kids_indoor_temp_rh_clean <- kids_indoor_temp_rh

# write_rds(kids_indoor_temp_rh_clean, "Output/kids_indoor_temp_rh_clean.rds")
```

>>>>

---
title: "KidsAIR indoor temp and humidity cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Clean up all temp/rh data
```{r}
kids_indoor_temp_rh <- read_rds("Output/kids_indoor_temp_rh.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

indoor_temp_rh_clean <- kids_indoor_temp_rh %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(indoor_temp_rh_clean, "Output/indoor_temp_rh_clean.rds")
```

# Summarize temp/rh data
```{r}
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")

temp_rh_summary <- indoor_temp_rh_clean %>%
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  t()
temp_rh_summary
```

### 2020-01-14 moisture_data_cleaning.Rmd
cleaning joining datasets begin summarizing data

---
title: "KidsAIR initial moisture content data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Clean up all moisture data
```{r}
kids_moisture <- read_rds("Output/kids_moisture.rds")

kids_moisture_clean <- kids_moisture

# write_rds(kids_moisture_clean, "Output/kids_moisture_clean.rds")
```

>>>>

---
title: "KidsAIR initial moisture content data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Clean up all moisture data
```{r}
kids_moisture <- read_rds("Output/kids_moisture.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

moisture_clean <- kids_moisture %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(moisture_clean, "Output/moisture_clean.rds")
```

### 2020-01-14 moisture_summary.Rmd
cleaning joining datasets begin summarizing data

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019"
output: pdf_document
---

@@

```{r}
# Load data
kids_moisture <- read_rds("Output/kids_moisture.rds")
```

# Summary stats
```{r}
summary_kids_moisture <- kids_moisture %>% 
  summarize(mean(pm_24hr_mean), sd(pm_24hr_mean),
            min(pm_24hr_mean), max(pm_24hr_mean),
            min(pm), max(pm),
            min(pm_sampling_days), max(pm_sampling_days),
            min(pm_total_observations), max(pm_total_observations)) %>% 
  t()
summary_kids_pm
```

# Boxplots
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- kids_pm %>% 
  ggplot(aes(area, pm_24hr_mean)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 400) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

>>>>

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
moisture_clean <- read_rds("Output/moisture_clean.rds")
```

# Summary stats
```{r}
summary_moisture <- moisture_clean %>% 
  group_by(area) %>% 
  summarize(mean(moisture_ave, na.rm = TRUE), sd(moisture_ave, na.rm = TRUE),
            median(moisture_ave, na.rm = TRUE),
            min(moisture_ave, na.rm = TRUE), max(moisture_ave, na.rm = TRUE)) %>% 
  t()
summary_moisture
```

# Boxplots
```{r, fig.height=6, fig.width=5}
boxplots_moisture <- moisture_clean %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 50) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Mean moisture content (%)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

### 2020-01-14 pm_summary.Rmd
cleaning joining datasets begin summarizing data

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 19 Dec 2019"
output: pdf_document
---

@@

```{r}
# Load data
kids_pm <- read_rds("Output/kids_pm_new.rds")
```

# Summary stats
```{r}
pm_summary <- kids_pm %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE))
```

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- kids_pm %>% 
  #filter(pm < 500) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

>>>>

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
pm_clean <- read_rds("Output/pm_clean.rds")
```

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(treatment) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE))
```

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- pm_clean %>% 
  #filter(pm < 500) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

### 2020-01-14 stove_grade_usage_cleaning.Rmd
cleaning joining datasets begin summarizing data

---
title: "KidsAIR wood stove grades and usage"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Clean up all stove grade data
```{r}
kids_stove_grades <- read_rds("Output/kids_stove_grades.rds")

kids_stove_grades_clean <- kids_stove_grades

# write_rds(kids_stove_grades_clean, "Output/kids_stove_grades_clean.rds")
```

@@

# Clean up all stove use data
```{r}
kids_stove_use <- read_rds("Output/kids_stove_use.rds")

kids_stove_use_clean <- kids_stove_use %>% 
  replace_with_na(replace = list(wood_cords = -999, wood_cords = 0))

# write_rds(kids_stove_use_clean, "Output/kids_stove_use_clean.rds")
```

>>>>

---
title: "KidsAIR wood stove grades and usage"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Clean up all stove grade data
```{r}
kids_stove_grades <- read_rds("Output/kids_stove_grades.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

stove_grades_clean <- kids_stove_grades %>% 
  filter(home_id != 0) %>% 
  rename(stove_grade_comments = comments) %>% 
  select(-home_id) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(stove_grades_clean, "Output/stove_grades_clean.rds")

# Dataset showing home with no stove grade
stove_grades_na <- stove_grades_clean %>% 
  filter(is.na(stove_grade)) %>% 
  distinct(home_id) 
```

# Summary data for stove grades
```{r}
# Load dataset
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")

stove_grade_summary <- stove_grades_clean %>% 
  group_by(area, stove_grade) %>% 
  summarize(n())
stove_grade_summary
```

@@

# Clean up all stove use data
```{r}
kids_stove_use <- read_rds("Output/kids_stove_use.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

stove_use_clean <- kids_stove_use %>% 
  replace_with_na(replace = list(wood_cords = -999, wood_cords = 0)) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(stove_use_clean, "Output/stove_use_clean.rds")
```

# Summary data for stove use
```{r}
# Load dataset
stove_use_clean <- read_rds("Output/stove_use_clean.rds")

# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  group_by(area) %>% 
  summarize(mean(wood_cords, na.rm = TRUE), 
            min(wood_cords, na.rm = TRUE), 
            median(wood_cords, na.rm = TRUE), 
            max(wood_cords, na.rm = TRUE))
stove_use_summary

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- stove_use_clean %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -wood_cords) 
lapply(table_list, table)

## Select specific var to assess individually/group by area
table(stove_use_clean$burn_level, stove_use_clean$area, useNA = "ifany")
```

### 2020-01-14 sums_data_cleaning.Rmd
cleaning joining datasets begin summarizing data

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 10 Jan 2020"
output: pdf_document
---

@@

# Continue cleaning up SUMs data
```{r}
all_sums_filtered <- read_rds("Output/all_sums_filtered.rds")

sums_clean <- all_sums_filtered %>% 
   mutate(temp_c_sums = as.numeric(temp_c_sums),
          winter_id = as.factor(winter_id),
          home_winter_id = as.factor(home_winter_id),
          home_id = as.factor(home_id),
          day_of_week = weekdays(date_sums),
          month_sums = as.factor(month(date_sums, label = TRUE, abbr = TRUE))) %>% 
  select(-filter_var) %>% 
  arrange(area, home, winter_id, datetime_sums)

>>>>

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Continue cleaning up SUMs data
```{r}
all_sums_filtered <- read_rds("Output/all_sums_filtered.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  select(home_winter_id, area, treatment)

sums_clean <- all_sums_filtered %>% 
   mutate(temp_c_sums = as.numeric(temp_c_sums),
          winter_id = as.factor(winter_id),
          home_winter_id = as.character(home_winter_id),
          home_id = as.factor(home_id),
          day_of_week = weekdays(date_sums),
          month_sums = as.factor(month(date_sums, label = TRUE, abbr = TRUE))) %>% 
  select(-filter_var) %>% 
  arrange(area, home, winter_id, datetime_sums) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))
